### 2023-08-17 manuscript.tex
Skip `manubot` update in "further updated" link [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/3bd352c60eea4ece353bd537273c44174cfb1d78.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/3bd352c60eea4ece353bd537273c44174cfb1d78/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/5891020105

\emph{A preprint of this manuscript is available at bioRχiv with the \href{https://doi.org/10.1101/2023.03.30.534917}{doi:10.1101/2023.03.30.534917}.}
\emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} (\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{archived here}) of the manuscript to \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
\emph{A revised version \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.1}{\texttt{v1.1}} (\href{https://habi.github.io/EAWAG-manuscript/v/c49d0b8ac8f078c226318972b06e8c4a39100bb2/}{archived here}) has been submitted.}
\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.1...37cc38a386f502ad80dd15509062ce55dc9330d8\#files_bucket}{is further updated} since re-submission.}

This manuscript
(\href{https://habi.github.io/EAWAG-manuscript/v/37cc38a386f502ad80dd15509062ce55dc9330d8/}{permalink})
was automatically generated
from \href{https://github.com/habi/EAWAG-manuscript/tree/37cc38a386f502ad80dd15509062ce55dc9330d8}{habi/EAWAG-manuscript@37cc38a}
on August 15, 2023.

@@

\leavevmode\vadjust pre{\hypertarget{ref-wsjdcTeC}{}}%
\CSLLeftMargin{15. }%
\CSLRightInline{OpenSCAD. {[}cited 15 Aug 2023{]}. Available: \url{https://openscad.org}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-wIfTDBqd}{}}%
\CSLLeftMargin{23. }%
\CSLRightInline{Image processing with Dask Arrays --- dask-image 2023.08.1+1.g86b56a7.dirty documentation. {[}cited 15 Aug 2023{]}. Available: \url{https://image.dask.org/en/latest/}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-rn6XbmFW}{}}%
\CSLLeftMargin{26. }%
\CSLRightInline{Teem: nrrd: Definition of NRRD File Format. {[}cited 15 Aug 2023{]}. Available: \url{https://teem.sourceforge.net/nrrd/format.html}}

>>>>

\emph{A preprint of this manuscript is available at bioRχiv with the \href{https://doi.org/10.1101/2023.03.30.534917}{doi:10.1101/2023.03.30.534917}.}
\emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} (\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{archived here}) of the manuscript to \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
\emph{A revised version \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.1}{\texttt{v1.1}} (\href{https://habi.github.io/EAWAG-manuscript/v/c49d0b8ac8f078c226318972b06e8c4a39100bb2/}{archived here}) has been submitted.}
\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/df99415...3bd352c60eea4ece353bd537273c44174cfb1d78\#files_bucket}{is further updated} since re-submission.}

This manuscript
(\href{https://habi.github.io/EAWAG-manuscript/v/3bd352c60eea4ece353bd537273c44174cfb1d78/}{permalink})
was automatically generated
from \href{https://github.com/habi/EAWAG-manuscript/tree/3bd352c60eea4ece353bd537273c44174cfb1d78}{habi/EAWAG-manuscript@3bd352c}
on August 17, 2023.

@@

\leavevmode\vadjust pre{\hypertarget{ref-wsjdcTeC}{}}%
\CSLLeftMargin{15. }%
\CSLRightInline{OpenSCAD. {[}cited 17 Aug 2023{]}. Available: \url{https://openscad.org}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-wIfTDBqd}{}}%
\CSLLeftMargin{23. }%
\CSLRightInline{Image processing with Dask Arrays --- dask-image 2023.08.1+1.g86b56a7.dirty documentation. {[}cited 17 Aug 2023{]}. Available: \url{https://image.dask.org/en/latest/}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-rn6XbmFW}{}}%
\CSLLeftMargin{26. }%
\CSLRightInline{Teem: nrrd: Definition of NRRD File Format. {[}cited 17 Aug 2023{]}. Available: \url{https://teem.sourceforge.net/nrrd/format.html}}
